\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-04-01 docs/paper/paper.tex
* System architecture diagram * Few fixes to the text

\documentclass[draft, a4, 10pt, onecolumn]{IEEEtran}

\usepackage{color,soul}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{cite}

@@

In this paper, we focus on estimating confinement loss, one of the propagation features of multi-channel Photonic Crystal Fiber (PCF) sensors, using artificial neural networks. Specifically, we have based our system on Surface Plasmon Resonance (SPR).

\hl{CK: Continuing from here...}

\hl{and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1). We will fix the pattern and geometrical shape of the cladding air holes, and vary the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$. Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional neural networks. }

\begin{figure}
\centering
\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{mainalgo.png}
\caption{}
\end{figure}

\hl{Literature survey}

@@

In this section details of the proposed method is discussed. At the start, a GAN is trained to generate additional data by using training samples. These generated samples are filtered to ensure they fall within the applicable range. Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network network. The details of the proposed ANN architecture and the GAN is discussed in the following subsections.

@@

>>>>

\documentclass[draft, a4, 10pt]{IEEEtran}

\usepackage{color,soul}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, shapes.arrows, decorations.markings, calc}
\usepackage{pgfplots}

\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{cite}

%for flowcharts
\tikzstyle{testing} = [
	thick,
	->,
	>=stealth
]
\tikzstyle{training} = [
	thick, 
	decoration={
		markings,
		mark=at position 1 with {
			\arrow[semithick]{open triangle 60}
		}
	},
	double distance=1.4pt, 
	shorten >= 5.5pt,
	preaction = {decorate},
	postaction = {
		draw,
		line width=1.4pt,
		white,
		shorten >= 4.5pt
	}
]

\tikzstyle{data} = [
	cylinder, 
	shape border rotate=90, 
	draw,
	minimum width=1.5cm, 
	minimum height=1.2cm,
	text centered, 
	draw=black, 
	line width=0.3mm,
	shape aspect=.1
]

\tikzstyle{operation} = [
	rectangle, 
	rounded corners,
	minimum width=2cm, 
	minimum height=1.2cm,
	text centered, 
	draw=black, 
	line width=0.6mm,
]

\tikzstyle{sample} = [
	rectangle, 
	minimum width=1.2cm, 
	minimum height=1.2cm,
	text centered, 
	draw=black,
	line width=0.3mm,
]

\tikzstyle{filter} = [
	trapezium, 
	trapezium left angle=70, 
	trapezium right angle=110, 
	minimum width=1.5cm, 
	minimum height=1cm, 
	text centered, 
	draw=black, 
	line width=0.5mm
]

@@

In this paper, we focus on estimating confinement loss, one of the propagation features of multi-channel Photonic Crystal Fiber (PCF) sensors, using artificial neural networks. Specifically, we have based our system on Surface Plasmon Resonance (SPR). However, in the experiments section we have demonstrated that the designed system is generic enough to apply to multiple PCF designs. Perhaps the most important contribution that augments the success of the proposed method is the use of GAN phase, where the available data is expanded to be used in the training phase.

\hl{!! Literature survey !!}

\hl{Use of ANN in PCF}

\hl{SPR in PCF}

@@

In this section details of the proposed method is discussed. At the start, a GAN is trained to generate additional data by using training samples. These generated samples are filtered to ensure they fall within the applicable range. Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network network. This architecture is illustrated in Figure \ref{fig:overall} The The details of the proposed ANN architecture and the GAN is discussed in the following subsections.

\begin{figure}
	\centering
	\begin{tikzpicture}[node distance=2cm]
\node (collected) [data] {Collected samples};
\node (GAN) [operation,below of=collected,xshift=-2cm] {GAN};
\node (filter) [filter, below of=GAN, text width=2.4cm] {\baselineskip=10pt Filter out-of-range samples\par};
\node (generated) [data, below of=filter] {Generated samples};
\node (ann) [operation,below of=generated,xshift=2cm] {ANN};
\node (testsample) [sample, right of=generated,xshift=2cm,yshift=-1cm, text width=1.2cm] {\baselineskip=10pt Test\par};
\node (output) [sample, below of=testsample,yshift=-0cm, text width=1.2cm] {\baselineskip=10pt Output\par};

\draw [training] (collected) -- (GAN);
\draw [training] (GAN) -- (filter);
\draw [training] (filter) -- (generated);
\draw [training] (generated) -- (ann);
\draw [training] (collected) -- (ann);
\draw [testing] (testsample.west) to [bend right=45] ($(ann.north east)-(0.5,0)$);
\draw [testing] ($(ann.south east)-(0.5,0)$) to [bend right=45] (output.west);
	\end{tikzpicture}
	\caption{System architecture}
	\label{fig:overall}
\end{figure}

@@

\hl{We will fix the pattern and geometrical shape of the cladding air holes, and vary the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$. Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional neural networks. }
